---
title: "ShipsDataPackage"
author: "Edward Gillian"
date: "27/05/2021"
output: github_document
always_allow_html: true
---


---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
<!-- badges: end -->

The `shipsdatapackage` has a number of goals: 


Firstly, this package uses `shiny.semantic` package from `Appsilon` to provide the ui interface.

Secondly, this package uses reactivity to get ship type and ship name input from the `ui` to display data about ship maximum distance and the start and end of ship movements.

Lastly, automated testing is done through chained test functions using `testthat`. These functions allow the developer to add different input files to test the functions stored in the `R` folder to be tested for reliable outputs. The functions use `expect_known_value` to generate the test outputs.

## Installation

You can install the released version of `shipsdatapackage` with:

```
devtools::install_github("EdwardJGillian/shipsdatapackage")
```

## Embedded Application

You can see the `shipsdatapackage` embedded in this document:

```{r ships_data, echo=FALSE}
library(shipsdatapackage)

appDir <- system.file("shiny-examples", "ships_app", package = "shipsdatapackage")

shiny::shinyAppDir(appDir,
  options = list(
  width = "100%", height = 550
  )
)
```

## Running the package

You can run `shipsdatapackage` by opening `global.R` in `shipsdatapackage/inst/shiny-examples/ships_app/`

or type in the console:

```
shipsdatapackage::run_ship_example()
```
