---
title: "ShipsDataPackage"
author: "Edward Gillian"
date: "27/05/2021"
output: github_document
always_allow_html: true
---


---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
<!-- badges: end -->

The `shipsdatapackage` has a number of goals: 


Firstly, this package uses `shiny.semantic` package from `Appsilon` to provide the ui interface.

Secondly, this package uses reactivity to get ship type and ship name input from the `ui` to display data about ship maximum distance and the start and end of ship movements.

Lastly, automated testing is done through chained test functions using `testthat`. These functions allow the developer to add different input files to test the functions stored in the `R` folder to be tested for reliable outputs. The functions use `expect_known_value` to generate the test outputs.

## Installation

You can install the released version of `shipsdatapackage` with:

```
devtools::install_github("EdwardJGillian/shipsdatapackage")
```

## Embedded Application

You can see the `shipsdatapackage` embedded in this document:

```{r ships_data, echo=FALSE}
library(shipsdatapackage)

appDir <- system.file("shiny-examples", "ships_app", package = "shipsdatapackage")

shiny::shinyAppDir(appDir,
  options = list(
  width = "100%", height = 550
  )
)
```

## Testing the package

As shown by the code below, a chained function using `purrr::map` is created to loop through a file list of example data to test the core functions  to be tested for reliable outputs. This function creates a series of reference files automatically

```
library(shipsdatapackage)
library(testthat)

test_chained_functions <- function(csv_file) {
  test_that("check file values for parameters", {
    # naming helper
    tname <- function(n) {
      paste0(home,
             "/data/known_value/",
             csv,
             ".",
             n,
             ".test"
      )
    }

    # create file path to csv file examples

    csv_path <-
      paste0(home, "/data/csv_examples/", csv_file)
    csv <- stringr::str_remove(csv_file, ".csv")
    df1 <- readr::read_csv(file=csv_path, col_names=TRUE, col_types = readr::cols())
    parameter_list <- shipsdatapackage::general_data_preprocess(df1)

    # SuppressWarnings used as expect_known_value is a deprecated function
    suppressWarnings(testthat::expect_known_value(
      parameter_list, tname("param_list")))

    frame_with_next_values <- cbind(df1[parameter_list$ranks,], next_lat = parameter_list$next_lat, next_lon = parameter_list$next_lon)

    frame_without_na <- frame_with_next_values[0:(nrow(frame_with_next_values)-1),]

    # rename columns by index to ensure column names are different
    frame_without_na <- frame_without_na %>%
      dplyr::rename(next_lat = 21, next_lon = 22)

    calc_distance <- mapply(shipsdatapackage::calculate_distance, frame_without_na$LON, frame_without_na$LAT, frame_without_na$next_lon, frame_without_na$next_lat)

    # SuppressWarnings used as expect_known_value is a deprecated function
    suppressWarnings(testthat::expect_known_value(
      calc_distance, tname("calc_dist")))


  })
}

# create the ALS file path
home <- setwd(Sys.getenv("HOME"))

csv_file_path <- file.path(home, "data/csv_examples")

csv_files_list <- list.files(path = csv_file_path, pattern = "*.csv$", full.names = FALSE)

# apply 1 list vector to the function
purrr::map(csv_files_list, test_chained_functions)

```

### Testthat results:

```{r tests}
library(testthat)
library(dplyr)
library(magrittr)
library(shipsdatapackage)
test_results_raw <- testthat::test_file("tests/testthat/test-chained_function_known_value.R", reporter = testthat::ListReporter)

test_results_individual <- test_results_raw %>%
  as_tibble() %>%
  dplyr::rename(Test = test) %>%
  dplyr::group_by(file, context, Test) %>%
  dplyr::summarise(NumTests = first(nb),
            Passed   = sum(passed),
            Failed   = sum(failed),
            Warnings = sum(warning),
            Errors   = sum(as.numeric(error)),
            Skipped  = sum(as.numeric(skipped)),
            .groups = "drop")

summarise_results <- function(res) {
  res %>% dplyr::summarise_if(is.numeric, sum) %>% knitr::kable()
  }

summarise_results(test_results_individual)
```

## Running the package

You can run `shipsdatapackage` by opening `global.R` in `shipsdatapackage/inst/shiny-examples/ships_app/`

or type in the console: `shipsdatapackage::run_ship_example()`

